Limited information strategies for topological games

### 2015-03-10 phd/talks-and-presentations/2015-03-11-defense.tex
add convergence game proofs

@@

>>>>

\begin{frame}{
  Proof that $\pl O\markwin \gruClusGameHard{\oneptcomp\omega_1}{\infty}$
}\small
  For each $\alpha<\omega_1$, let $f_\alpha:\alpha\to\omega$ be injective.

  Note that for each $F\in[\omega_1]^{<\omega}$, there is some $n_F<\omega$
  such that $f_{\alpha+1}(\beta)<n_F$ for all $\beta,\alpha\in F$.

  Let $\sigma$ be a Markov strategy for $\pl O$ such that
    \[
      \sigma(\<\alpha\>,n)
        \subseteq
      \oneptcomp\omega_1 \setminus
      \{\beta<\omega_1:f_{\alpha+1}(\beta)<n\}
    \]
  for $\alpha<\omega_1$.

  Thus as any legal counterattack cannot have finite range in $\omega_1$
  without repeating $\infty$ co-finitely,
  $\sigma$ is a winning Markov strategy. $\qed$
\end{frame}

\begin{frame}{
  Proof that $\pl O\nottactwin\gruClusGameHard{\oneptcomp\omega_1}{\infty}$
}\small
  Let $\sigma$ be a tactic for $\pl O$ in
  $\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.

  Then this set is closed and unbounded in $\omega_1$:
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_1
          :
        \beta<\alpha
          \Rightarrow
        \oneptcomp\omega_1\setminus\sigma(\<\beta\>)
        \subseteq \alpha
      \}
    \]

  If $a_\sigma:\omega_1\to C_\sigma$ is an order isomorphism, then
  there is $n<\omega$ such that $a_\sigma(n)\in\sigma(\<a_\sigma(\omega)\>)$.

  Then since $a_\sigma(\omega)>a_\sigma(n)$ implies
  $a_\sigma(\omega)\in\sigma(\<a_\sigma(n)\>)$
  (by the definition of $C_\sigma$), it follows that
  $\<a_\sigma(n),a_\sigma(\omega),a_\sigma(n),a_\sigma(\omega),\dots\>$
  is a legal counterattack against $\sigma$ which does not cluster at
  $\infty$. $\qed$
\end{frame}

@@

\section{}
